---
name: Scott Isaac Large
position: "Chief, Ecosystem Dynamics and Assessment Branch"
address: "NOAA-Fisheries, 166 Water Street, Woods Hole, Massachusetts, 02543"
phone: +1 ‪(508)499-9833‬
email: "scott.large@noaa.gov | largesi@gmail.com"
twitter: ScottLarge_
github: slarge
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
header_includes:
  - \ExecuteBibliographyOptions{useprefix=true}
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(rorcid)
library(RefManageR)
source("Rpackages.R")
source("baretable.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r packages, include=FALSE}
write_packages_bib(
 pkglist = c("fedregs"),
 file = "Rpackages.bib")
```

# Education

```{r degrees, results='asis'}
tribble(
  ~Year, ~Degree, ~Institution,
  2006, "B.A. Biology", "Hendrix College",
  2008, "M.S. Biology", "Texas A\\&M University -- Corpus Christi",
  2011, "Ph.D. Marine Biology", "Texas A\\&M University",
) %>%
  arrange(-Year) %>%
  baretable()
```


# Employment history
```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2011, 2014, "\\textbf{Postdoctoral Researcher}, Integrated Statistics, Inc \\& Northeast Fisheries Science Center",
  2014, 2018, "\\textbf{Professional Officer}, Advice Department -- International Council for the Exploration of the Sea (ICES)",
  2018, NA, "\\textbf{Chief}, Ecosystem Dynamics and Assessment Branch -- Northeast Fisheries Science Center"
) %>%
  arrange(-Start) %>%
  #filter(Start > 2000) %>%
  mutate(End = as.character(End),
         End = replace_na(End, "present")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Position) %>%
  baretable()
```

## Other positions

```{r positions, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2017, 2017, "\\textbf{Stock Assessment Consultant}, United Nations Food and Agriculture Organization (FAO)",
  2019, NA, "\\textbf{Associate Editor}, \\textit{Frontiers in Marine Science}",
  2022, NA, "\\textbf{Adjunct faculty}, Massachusetts Maritime Academy",
) %>%
  arrange(desc(Start)) %>%
  mutate(End = as.character(End),
    End = replace_na(End, "present")) %>%
  mutate(Year = paste(Start, "–", End, sep = "")) %>%
  select(Year, Position) %>%
  baretable()
```


# Publications

## PhD thesis
```{r thesis}
bibliography_entries("large_pubs.bib") %>% #, startlabel = "papersstart") %>%
  filter(tolower(genre) == "phd thesis")
```

## Selected research papers
<!-- In review: Badger et al, Saba et al,  *  -->
```{r research-papers}
 bibliography_entries("large_pubs.bib") %>%
   filter(tolower(type) == "article-journal") %>%
  tail(15) %>% 
  arrange(desc(issued), author)

```

## Software (R packages)
```{r r-packages}
# Sort R packages by title, then year.
bibliography_entries("Rpackages.bib") %>% 
  arrange(title, issued)
```

# Presentations
## Invited talks
 * Invited speaker, *Transitioning basic research into applied fisheries science and management*, Dauphin Island Sea Lab, Dauphin Island, November 2022.
 * Workshop leader, *Delineating the Issues of Climate Change and Impacts to Marine Ecosystems: Bridging the Gap Between Research, Assessment, Policy and Management*, IMBER--ClimEco4, Shanghai, June 2014.
 * Workshop leader, *Introduction to Generalized Additive Modeling*, RARGOM--Community Learning Series,  Woods Hole, April 2013
 * Invited speaker, *Quantifying trends and thresholds in responses of ecological indicators to the combined effects of fishing and environmental pressures*, Colorado State University, Fort Collins, March 2013
 * Invited speaker, *Delineating ecosystem overfishing via analysis of ecosystem indicator inflection points*, 2nd ICES/PICES conference for early career scientists. Mallorca, April 2012

<!-- ## Selected contributed talks -->
<!--  *  -->

# Awards
```{r grants}
grants <- read_csv("Grant_income.csv", show_col_types = FALSE)
```

```{r awardstable, results = "asis"}
grants %>%
  filter(Type %in% c("Award")) %>%
  mutate(
    Time = paste0(Start, ifelse(is.na(End),"",paste0("--",End))),
    Entry = Source,
    Amount = ifelse(is.na(Amount),
                    "—", 
                    paste("\\$", prettyNum(Amount, big.mark=","), sep=""))
  ) %>%
  arrange(Time, desc(Amount)) %>%
  select(Time, Entry, Amount) %>%
  baretable(align='llp{13.3cm}r',
            hline.after= NULL, #c(0,NROW(.)),
            size="\\fontsize{10}{16}",
            add.to.row=list(
              pos=as.list(seq(NROW(.))),
              command=rep("\\\\[-0.2cm]",NROW(.))))

```


# Grants
```{r grantstable, results='asis'}
# filter(Type %in% c("Research"))

grants %>%
  filter(Type %in% c("Research")) %>%
  mutate(
    Time = paste0(Start, ifelse(is.na(End),"",paste0("--",End))),
    Entry = paste(People, ". ``", Title, "''. ",
                  "\\emph{Funding from ", Source,"}",
                  sep=""),
    Amount = paste("\\$",prettyNum(Amount, big.mark=","), sep="")
  ) %>%
  arrange(Time, desc(Amount)) %>%
  select(Time, Entry, Amount) %>%
  baretable(align='llp{13.3cm}r',
            hline.after= NULL, #c(0,NROW(.)),
            size="\\fontsize{10}{16}",
            add.to.row=list(
              pos=as.list(seq(NROW(.))),
              command=rep("\\\\[-0.2cm]",NROW(.))))

```




##
